Fixing Vulnerabilities Hinders Maintainability (REG)

### 2019-05-09 paper/ICPC19/icpc19.tex
mapping finished

\textbf{Write Clean Code} & Avoid producing software with code smells because
it is more likely to be maintainable in the future & Help ? \\
\bottomrule
\end{tabular}
\vspace{-0.5cm}
\label{tab:guidelines}
\end{table}

>>>>

\textbf{Write Clean Code} & Avoid producing software with code smells because
it is more likely to be maintainable in the future & \textbf{Code Smells:} \# of Occurrences~\cite{Visser:2016:OREILLY} (e.g., magic constants and long identifier names) \\
\bottomrule
\end{tabular}
\vspace{-0.5cm}
\label{tab:guidelines}
\end{table}
